Verifying Demonstrations

### 2017-11-20 contents-poster.tex
Minor updates
- Removes hint from fig 1.
- Adds location icon and "Protest ended" to comic for clarification.
Adds space in the middle

    \begin{figure}
      \centering
      \includegraphics[width=0.9\linewidth]{fig/trump.jpg}
      \caption{%
        What can we trust?
        (Hint: not much.)
        Image: Reddit/The\_Donald, Twitter.
      }\label{TrumpInauguration}
    \end{figure}

@@

    \begin{greenblock}{Our approach}
      \begin{itemize}
        \item Provides a \emph{lower bound} of the participation count.
        \item Provides a verifiable participation count.
        \item Provides privacy based on anonymous credentials.
        \item The only added risk (over not using this) is if someone can use 
          your secret key.
        \item Requires only local connectivity during the protest.
      \end{itemize}
    \end{greenblock}

@@

>>>>

    \begin{figure}
      \centering
      \includegraphics[width=0.9\linewidth]{fig/trump.jpg}
      \caption{%
        What can we trust?
        This picture was posted on Twitter (and linked from Reddit) to argue 
        that the news reporting on the participation count was \enquote{fake 
          news} and that Trump's supporters arrived later.
        Even if the picture labelled \enquote{REALITY} would be from the same 
        event (difficult to verify), it is difficult to accurately compare due 
        to the angle.
        Image: Reddit/The\_Donald, Twitter.
      }\label{TrumpInauguration}
    \end{figure}

@@

    \begin{greenblock}{Our approach}
      \begin{itemize}
        \item Provides a \emph{lower bound} of the participation count.
        \item This lower bound is cryptographically verifiable.
        \item Provides privacy based on anonymous credentials.
        \item The only added risk (over not using this) is if someone can use 
          your secret key.
        \item Requires only local connectivity during the protest.
        \item Requires no trust in the source (as in \cref{TrumpInauguration}), 
          only that IDs are issued correctly.
      \end{itemize}
    \end{greenblock}

@@

\vfill
\vspace{8cm}
